### 2017-11-01 paper/sections/1_introduction.tex
paper: edits, viz: add Dockerfile
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is Mantle
To solve this problem, we integrate Mantle into
ParSplice~\cite{perez:jctc20150parsplice}. Mantle is a dynamic policy engine
that decomposes complicated services into manageable pieces so developers
unfamiliar with a code-base can reason about its behavior. Administrators use
the framework to describe ``when" they want data moved, ``where" they want data
moved, and ``how much" of the data to move.  This abstraction helps developers
unfamiliar with the domain quickly reason about, develop, and deploy new
policies that control temporal and spatial locality. It has already proven to
be a critical control plane for improving file system metadata load
balancing~\cite{sevilla:sc15-mantle} and in this work we show its usefulness in
cache management.

>>>>

% What is Mantle
To solve this problem, we integrate Mantle into
ParSplice~\cite{perez:jctc20150parsplice}. Mantle is a dynamic policy engine
that decomposes complicated services into manageable pieces, where developers
write policies for ``when" they want data moved, ``where" they want data moved,
and ``how much" of the data to move.  The framework then executes these
policies whenever a decision needs to be made.  This abstraction helps
developers unfamiliar with the domain quickly reason about, develop, and deploy
new policies that control temporal and spatial locality. It has already proven
to be a critical control plane for improving file system metadata load
balancing~\cite{sevilla:sc15-mantle} and in this work we show its usefulness in
cache management.

### 2017-11-01 paper/sections/4_dynamic-policies.tex
paper: edits, viz: add Dockerfile
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsubsection{Regime Detection}
\subsubsection{Trajectory Length}

>>>>

\subsubsection{Regime Detection}

At each time step, we find the lowest ID and compare against the local minima,
which is the smallest ID we have seen thus far. If we move left to right, the
local minima never changes because the local minima will start small. If we
move from right to left, the local minima changes at each access regime.  For
points \(z\), \(y\), and \(x\), if the local minimum is the same we are in a
regime. Processing \(y\), we set the local minima to be \(min(y, m_l)\), where
\(m_l\) is the local minima of the previous time step of \(z\).

This
raises false positives for regime changes

\begin{figure}[tb]
\begin{minted}[linenos]{lua}
local function when()

  if servers[whoami]["load"] > target then
    if servers[whoami]["load"] > absorb_target then
      WRstate(1)
    end
    if RDstate() == 1 then
      return true
    end
  end
  return false
end
\end{minted}
\caption{ParSplice cache management policy.\label{lua:parsplice}}
\end{figure}

\subsubsection{Trajectory Length}
